---
title: "HW 02 - Majors + legos"
author: "INSERT NAME HERE"
date: "`r Sys.Date()`"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(dsbox) 
library(fivethirtyeight)
library(scales)
```


### Exercise 1

#### Narrative

Remove this text, and add your answer for Exercise 1 here.

### Exercise 2

#### Code

```{r majors-median-5000}
# remove this comment and add the code for Exercise 2 here
```

### Exercise 3

#### Code

```{r majors-median-1000}
# remove this comment and add the code for Exercise 2 here
```

#### Narrative

Remove this text, and add your answer for Exercise 3 here.


### Exercise 4

#### Code

```{r non-stem-salaries}
# remove this comment and add the code for Exercise 4 here
```

#### Narrative

Remove this text, and add your answer for Exercise 4 here.


### Exercise 5

#### Code

```{r pick-your-own}
# remove this comment and add the code for Exercise 4 here
```

#### Narrative

Remove this text, and add your answer for Exercise 5 here.


### Exercise 6

#### Code

```{r most-money}
# remove this comment and add the code for Exercise 4 here
```

#### Narrative

Remove this text, and add your answer for Exercise 6 here.


### Exercise 7

#### Code

```{r area-code}
# remove this comment and add the code for Exercise 4 here
```

#### Narrative

Remove this text, and add your answer for Exercise 7 here.
